Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex
worked on intra-team work stuff

The following sections describe the architecture and function of each of the aforementioned subsystems in detail. The detection subsystem is broken up into two parts: Automobile Detection (section 3.1) and License Plate Image Acquisition (section 3.2). The server subsystem is also broken into two parts: Server Processing (section 3.4) and Web Application (section 3.5). Lastly, section 3.3 discusses the Central Base Station.

@@

\begin{enumerate}
\item Front-facing, publicly-accessible "Smartlots" website,
\item Back-end HTTP interface,
\item MySQL database, and
\item Administrator website
\end{enumerate}

@@

This work described in this project was completed by six people. The four authors contributed the bulk of the work ( >90\%), and two ACMx group members also helped us, mainly by getting us up to speed on the state of the ACMx project when we started, and continuing to be our points of contact to the ACMx group. The work was broken down as follows:

@@

Santiago worked primarily with the hardware needed to get this system working. He built the sensor nodes that include both the Arduino Fio and the Raspberry Pi. He deployed the code written by Roy Stilwell to the Arduino Fios, modifying slightly to suit our purposes. He also did most of the work deploying code to the image Acquisition Raspberry Pis, and he was the one that wrote the script that makes the Pis take an image when the magnetometer detects a car.

>>>>

The following sections describe the architecture and function of each of the aforementioned subsystems in detail. The detection subsystem is broken up into two parts: Automobile Detection (section 3.1) and License Plate Image Acquisition (section 3.2). The glue between the sensors and the server is the Central Base Station (section 3.3). The server subsystem is also broken into two parts: Server Processing (section 3.4) and Web Application (section 3.5).

@@

\begin{enumerate}
\item Front-facing, publicly-accessible "Smartlots" website,
\item Back-end HTTP interface,
\item MySQL database, and
\item Administrator website.
\end{enumerate}

@@

This work described in this project was completed by six people. The four authors of this paper contributed the bulk of the work ( >90\%), and two ACMx group members also helped us, mainly by getting us up to speed on the state of the ACMx project when we started, and continuing to be our points of contact to the ACMx group. The work was broken down as follows:

@@

Santiago Gonzalez worked primarily with the hardware needed to get this system working. He built the sensor nodes that include both the Arduino Fio and the Raspberry Pi. He deployed the code written by Roy Stilwell to the Arduino Fios, modifying slightly to suit our purposes. He also did most of the work deploying code to the image Acquisition Raspberry Pis, and he was the one that wrote the code that makes the Pis take an image when the magnetometer detects a car. His work is described in section 3.1.

\textbf{ACMx Group Members}

Roy Stilwell is the head of the ACMx group. Although he wasn't available to help us very much during the course of this project, much of what he and the other ACMx group members did laid the groundwork for what we accomplished in our project. The code that is listed below that runs on the Arduino Fios was written almost entirely by Roy. Roy also designed the Smartlots webpage, and wrote some of the code that is used on the base station Raspberry Pi.

Drew Koelling was a huge help to our group during this project. He met with us several times during our hackathon, even though he did not have as much stake in the success of this project, given that his grade did not depend on what we got done. He primarily helped us understand the base station code, and the existing web interface, and provided Taylor with the information necessary to create a useful REST API. He also helped rewrite some of that base station code. He was overall a great point of contact between our group and the ACMx group, and he was very helpful and good-natured the whole time. We want to explicitly thank him for all the help he gave us in this project.
